Mining Scenario/Transaction Pairs in HW/SW Co-verification Using Symbolic Execution

### 2017-04-07 paper.tex
spelling

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %                     Handling Semantic Gap  
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Generating a unified FW-HW model for co-verification is a 
well-known technique to handle the semantic mismatch between  
HW~\footnote{Note that whenever we refer to ``hardware'' 
from this point onwards, we mean an RTL implementation 
and not a TLM.}  and FW models.  Most of the existing techniques 
for constructing a unified FW-HW model~\cite{fmsd02,emsoft07,fase10} 
are not useful in practise for three reasons -- 1) use of abstract HW models 
instead of RTL implementation, 2) the unified model
construction is agnostic to the underlying reasoning engine, and 3) 
the unified model does not leverage property specification over the
interaction between a FW and HW, hence ineffective for practical co-verification.  
We will call the unified FW-HW model as \emph{co-verification model}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %                        Concurrency   
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
A co-design system is comprised of a set of concurrent FW and HW transactions 
which interleaves asynchronously. It is well recognized that concurrency is at
the heart of co-verification. The number of interleavings between the FW
and HW threads can be large, which can become a bottleneck in the
verification process.  However, we observe that in practice, 
producer-consumer relationship is prevelant in many industrial 
co-designs~\cite{polig2014micro,polig2014fpl,giefers2015accelerating} --
the master module (producer) solely updates the shared registers which are
consumed by the slave (consumer).  This key observation allows us to
sequentialize concurrent FW and HW transactions that follow specific interaction
patterns.  This drastically reduces the total number of interleavings 
between a FW and HW threads and simplies the overall complexity of the 
verification task. 
%
%===============================================================================
%\subsection{Contributions}
%===============================================================================
In this paper, we make the following contributions:
\begin{enumerate}

@@

We verify a total of 7 transaction level propertes and 12 

@@

We check whether the acknowledgment for data transmission and data reception arrives

@@

% ===============================================================================
\section{Limitations of Proposed Approach}
% ===============================================================================
The primary motivation for constructing a sequential single threaded unified 
co-verification model is to avoid enumerating exponential number of interleavings 
between the HW and FW threads.  We have shown that this is extremely beneficial for 
co-designs that exhibits producer-consumer relationship.  
In particular, our path-based algorithm in \verifox is able to suitably exploit 
this interaction behavior in a sequential co-verification model through symbolic 
execution by generating relevant scenario/transaction pairs.  However, this approach 
is not applicable for co-designs that exhibits true concurrency~\cite{codesign}, 
that is, a FW and its interacting HW threads do not show producer-consumer relationship.  
In this case, it is imperative to consider all possible interleavings between participating 
threads in an efficient manner.  To the best of our knowledge, the producer-consumer 
interaction pattern is prevelant in many practical 
co-designs~\cite{polig2014micro,polig2014fpl,giefers2015accelerating,hvc}.

@@

In practise, a FW exercises only a fragment of the HW state-space for a given scenario.  
This renders many interactions between HW and FW transactions infeasible.   
Our general observation is that bounded model checking technique in \hwcbmcv 
cannot prune irrelevant transactions with respect to a given scenario, 
and hence generate a monolithic co-verification model, which are often 
extremely difficult to solve with a SAT/SMT solver. On the other hand, 
a path-based exploration strategy in \verifox is able to automatically 
mine relevant scenario/transaction pairs in a sequential co-verification 
model, owing to specific optimizations such as eager path pruning
combined with incremental SAT solving.  Our experiments show that \verifox 
is an order of magnitude faster than \hwcbmcv for proving safety as well as 
bug finding.  In the future, we plan to extend our framework to co-design 
models that exhibit further interaction patterns.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %                     Handling Semantic Gap  
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Generating a unified FW-HW model for co-verification is a 
well-known technique to handle the semantic mismatch between  
HW~\footnote{Note that whenever we refer to ``hardware'' 
from this point onwards, we mean an RTL implementation 
and not a TLM.}  and FW models.  Most of the existing techniques 
for constructing a unified FW-HW model~\cite{fmsd02,emsoft07,fase10} 
are not useful in practice for three reasons -- 1) use of abstract HW models 
instead of RTL implementation, 2) the unified model
construction is agnostic to the underlying reasoning engine, and 3) 
the unified model does not leverage property specification over the
interaction between a FW and HW, hence ineffective for practical co-verification.  
We will call the unified FW-HW model as \emph{co-verification model}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %                        Concurrency   
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
A co-design system is comprised of a set of concurrent FW and HW transactions 
which interleaves asynchronously. It is well recognized that concurrency is at
the heart of co-verification. The number of interleavings between the FW
and HW threads can be large, which can become a bottleneck in the
verification process.  However, we observe that in practice, 
producer-consumer relationship is prevalent in many industrial 
co-designs~\cite{polig2014micro,polig2014fpl,giefers2015accelerating} --
the master module (producer) solely updates the shared registers which are
consumed by the slave (consumer).  This key observation allows us to
sequentialize concurrent FW and HW transactions that follow specific interaction
patterns.  This drastically reduces the total number of interleavings 
between a FW and HW threads and simplifies the overall complexity of the 
verification task. 
%
%===============================================================================
%\subsection{Contributions}
%===============================================================================
In this paper, we make the following contributions:
\begin{enumerate}

@@

We verify a total of 7 transaction level properties and 12 

@@

We check whether the acknowledgement for data transmission and data reception arrives

@@

% ===============================================================================
\section{Limitations of Proposed Approach}
% ===============================================================================
The primary motivation for constructing a sequential single threaded unified 
co-verification model is to avoid enumerating exponential number of interleavings 
between the HW and FW threads.  We have shown that this is extremely beneficial for 
co-designs that exhibits producer-consumer relationship.  
In particular, our path-based algorithm in \verifox is able to suitably exploit 
this interaction behavior in a sequential co-verification model through symbolic 
execution by generating relevant scenario/transaction pairs.  However, this approach 
is not applicable for co-designs that exhibits true concurrency~\cite{codesign}, 
that is, a FW and its interacting HW threads do not show producer-consumer relationship.  
In this case, it is imperative to consider all possible interleavings between participating 
threads in an efficient manner.  To the best of our knowledge, the producer-consumer 
interaction pattern is prevalent in many practical 
co-designs~\cite{polig2014micro,polig2014fpl,giefers2015accelerating,hvc}.

@@

In practice, a FW exercises only a fragment of the HW state-space for a given scenario.  
This renders many interactions between HW and FW transactions infeasible.   
Our general observation is that bounded model checking technique in \hwcbmcv 
cannot prune irrelevant transactions with respect to a given scenario, 
and hence generate a monolithic co-verification model, which are often 
extremely difficult to solve with a SAT/SMT solver. On the other hand, 
a path-based exploration strategy in \verifox is able to automatically 
mine relevant scenario/transaction pairs in a sequential co-verification 
model, owing to specific optimizations such as eager path pruning
combined with incremental SAT solving.  Our experiments show that \verifox 
is an order of magnitude faster than \hwcbmcv for proving safety as well as 
bug finding.  In the future, we plan to extend our framework to co-design 
models that exhibit further interaction patterns.
